Write-and-f-array: implementation and an application

### 2013-09-12 msc.tex
work

An object we will predominantly use in this paper is a CAS (Compare-And-Swap) register.
We will specify its semantics by providing pseudocode which correctly implements this object in
a single-threaded program (this will be our method of choice of providing object's semantics):

@@

\begingroup\let\clearpage\relax\chapter{Acknowledgements}\endgroup
The author would like to thank his advisor, dr. Grzegorz Herman for many fruitful discussions and help while preparing this paper. He would also like to thank Szymon Acedański for his help in improving the presentation of this paper.

>>>>

An object we will predominantly use in this work is a CAS (Compare-And-Swap) register.
We will specify its semantics by providing pseudocode which correctly implements this object in
a single-threaded program (this will be our method of choice of providing object's semantics):

@@

\begingroup\let\clearpage\relax\chapter{Acknowledgements}\endgroup
The author would like to thank his advisor, dr. Grzegorz Herman for many fruitful discussions and help while preparing this work. He would also like to thank Szymon Acedański for his help in improving the presentation of this work.
